Supplement 1: Testing different distributions

### 2018-09-22 pkg/disttree/inst/draft/supplement/supplement_distributions.Rnw
revised versions of supplements with corresponding reproduction files
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2289 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 443c37f89e7b5b3420a6e5a3862fb100989d9f2d

In Figure~\ref{fig:box_crpss_gaussian} the tested distributions are compared 
for each method based on CRPS skill score with the censored Gaussian distribution 
as reference represented by the horizontal line at zero. Again, the forest model 
and the EMOS show only slight variations (on average not even 1\%) over different 
distributions while the two GAMLSS models perform even or slightly better applying 
a hurdle model and loose strength when employing a logistic distribution compared 
to a Gaussian distribution.

@@

Altogether it can be stated that the left-censored at zero Gaussian distribution seems 
to be an appropriate choice while the other two distributions, especially the hurdle model, 
are also reasonable alternatives. However, they do not lead to an overall improvement in 
performance for this application.

@@

# CRPS skill score for boosted hgaussian
c_hgaussian <- matrix(ncol = 4, nrow = 15)
c_hgaussian[,1] <- means[means$method == "Distributional forest" & means$distribution == "hgaussian", "crps"]
c_hgaussian[,2] <- means[means$method == "Prespecified GAMLSS" & means$distribution == "hgaussian", "crps"]
c_hgaussian[,3] <- means[means$method == "Boosted GAMLSS" & means$distribution == "hgaussian", "crps"]
c_hgaussian[,4] <- means[means$method == "EMOS" & means$distribution == "hgaussian", "crps"]

# CRPS skill score for prespecified logistic
c_logistic <- matrix(ncol = 4, nrow = 15)
c_logistic[,1] <- means[means$method == "Distributional forest" & means$distribution == "logistic", "crps"]
c_logistic[,2] <- means[means$method == "Prespecified GAMLSS" & means$distribution == "logistic", "crps"]
c_logistic[,3] <- means[means$method == "Boosted GAMLSS" & means$distribution == "logistic", "crps"]
c_logistic[,4] <- means[means$method == "EMOS" & means$distribution == "logistic", "crps"]

>>>>

In Figure~\ref{fig:box_crpss_gaussian} the tested distributions are compared 
for each method based on CRPS skill score with the censored Gaussian distribution 
as reference represented by the horizontal line at zero. Again, the forest model 
and the EMOS show only slight variations (on average not even one percent) over different 
distributions while the two GAMLSS models perform even or slightly better applying 
a hurdle model and loose strength when employing a logistic distribution compared 
to a Gaussian distribution.

@@

Altogether it can be stated that for this application the left-censored at zero Gaussian distribution seems 
to be an appropriate choice while the other two distributions, especially the hurdle model, 
are also reasonable alternatives. However, they do not lead to an overall improvement in 
performance for this application.

@@

# CRPS for hgaussian
c_hgaussian <- matrix(ncol = 4, nrow = 15)
c_hgaussian[,1] <- means[means$method == "Distributional forest" & means$distribution == "hgaussian", "crps"]
c_hgaussian[,2] <- means[means$method == "Prespecified GAMLSS" & means$distribution == "hgaussian", "crps"]
c_hgaussian[,3] <- means[means$method == "Boosted GAMLSS" & means$distribution == "hgaussian", "crps"]
c_hgaussian[,4] <- means[means$method == "EMOS" & means$distribution == "hgaussian", "crps"]

# CRPS for logistic
c_logistic <- matrix(ncol = 4, nrow = 15)
c_logistic[,1] <- means[means$method == "Distributional forest" & means$distribution == "logistic", "crps"]
c_logistic[,2] <- means[means$method == "Prespecified GAMLSS" & means$distribution == "logistic", "crps"]
c_logistic[,3] <- means[means$method == "Boosted GAMLSS" & means$distribution == "logistic", "crps"]
c_logistic[,4] <- means[means$method == "EMOS" & means$distribution == "logistic", "crps"]
